\section{Predicting behavior in novel strategic games}
\label{sec:predict_new_AR}

Thus far, we have argued that theory-grounded \persona{s}, validated on distinct but related datasets, offer an approach for predicting human responses in entirely novel settings.
To empirically test the efficacy of our approach, we now turn to predicting human behavior in a set of strategic games adapted from \cite{1120Arad2012}'s (AR) study of strategic reasoning.

We begin by briefly reviewing the level-$k$ model of strategic reasoning that originally motivated AR. 
This model provides plausible theoretical underpinnings linking the training, testing, and novel games in this section.
We then describe the structure of the original 11-20 money request game and outline our procedure for constructing theory-grounded \aisub{s}: optimizing their parameters on human data from AR's original experiment, and validating their predictive performance on distinct but related variants also studied by AR.
Finally, we introduce an entirely new set of games adapted from AR's original design but featuring distinct numeric ranges and a novel participant sample recruited from Prolific. 
Agents are evaluated on their ability to predict human behavior in these never-before-seen games. 

Although this section focuses on strategic reasoning games, the same procedure can be applied in any setting.
In Appendix \ref{app:predict_new_CR}, we replicate the process using the allocation games from \cite{charness2002understanding}, which explore social preferences.
Two other important differences in that section are that we: (i) optimize across multiple related settings rather than a single training setting, and (ii) utilize the construction method to build agents.
We also present an additional preregistered experiment with human subjects to validate these agents in new settings.

