\section{Predicting behavior in novel allocation games}
\label{app:predict_new_CR}

We further test the robustness of our approach by predicting human behavior on a set of novel allocation games.
Unlike the strategic reasoning games studied in Sections~\ref{sec:predict_new_AR} and \ref{sec:ext-valid}, these games---adapted from \cite{charness2002understanding}'s (CR) experiments on social preferences---require individuals to balance their own monetary payoffs against those of others. 
They offer a distinct theoretical and empirical context for validating the generalizability of \persona{s} identified using our approach.
In addition to this new context, there are two key technical differences from the previous section.
First, samples of agents are optimized over several training settings simultaneously.
This further decreases the likelihood of overfitting on idiosyncratic features of any particular setting.
Second, we employ the novel construction method and parameterize a prompt template to optimize the agents in-sample.

We follow the same analytical structure and use similar notation as in Section~\ref{sec:predict_new_AR}.
We first briefly describe the dictator settings originally explored by CR, as these form our training dataset. 
Next, we detail our procedure for optimizing samples of \aisub{s}, where the motivating theory is drawn directly from the social-preference models in CR. 
We then validate these subjects on a distinct set of two-player games studied by CR and demonstrate the pitfalls of optimizing over atheoretical \persona{s}.
Finally, we introduce a new series of structurally distinct three-player allocation games and use them to illustrate the empirical efficacy of our approach in novel games that were not in the LLM's training corpus.
