\section{Harsanyi-Selten selector implementation details}
\label{app:nash-selector}

Let $E$ be the finite set of Nash equilibria of a simultaneous, two-player normal-form game that is symmetric, so that the row player's payoff matrix is $U$ and the column player's payoff matrix is $U^\top$.
\cite{HarsanyiSelten1988}'s four-stage procedure deterministically selects a single equilibrium.
For the vast majority of games in our setting, an equilibrium is selected in one of the first three steps.
The fourth is barely used and is more a formality.

Our implementation follows that blueprint with two minimal deviations that (1) protect symmetric components in the Pareto filter and (2) enforce symmetry in the reported profile after tracing.
The procedure deterministically returns a single selection; in symmetric games, and when the tracing routine returns normally, the selected profile is symmetric.
The code is or will soon be available at \url{https://benjaminmanning.io/}.
The following pseudocode broadly outlines the procedure.

\paragraph{Step 1 (component decomposition).}
Two equilibria $e=(\sigma^r,\sigma^c)$ and $e'=(\tau^r,\tau^c)$ are adjacent when they differ in exactly one player's strategy.
The connected components of the resulting graph---call them $C_1,\dots,C_K$---are the equilibrium components.

\paragraph{Step 2 (Pareto filter with symmetry safeguard).}
For each component $C_k$ compute its security vector $v(C_k)=\bigl(\min_{e\in C_k}u_1(e),\,\min_{e\in C_k}u_2(e)\bigr)$, where $u_1(e)=\sigma^{r\top}U\sigma^c$ and $u_2(e)=\sigma^{r\top}U^\top\sigma^c$.
Delete $C_k$ if some $C_\ell$ is strictly better in both coordinates. 

\paragraph{Step 3 (symmetry filter and risk dominance).}
Discard all remaining components that contain no symmetric equilibrium.
If multiple components survive, choose the one whose representative symmetric equilibrium (the first symmetric equilibrium encountered when iterating the component) minimizes the risk-dominance index
\[
R(\sigma)=\sum_{i\neq j}\sigma_i\sigma_j\,
\bigl[U_{ii}-U_{ji}\bigr]\bigl[U_{ii}-U_{ij}\bigr].
\]
If two or more symmetric components attain exactly the same minimal value, we keep the first one encountered in iteration order.
If no symmetric components remain after the symmetry filter, we select the first Pareto-surviving component as a fallback before Step~4.

\paragraph{Step 4 (alpha-tracing).}
Let the winning component be the one selected in Step~3 (or the
first Pareto-surviving component if no symmetric component remains).
\begin{itemize}
\item If the winning component is a singleton that already contains a
symmetric equilibrium, we return it directly (no tracing).
\item Otherwise, we run Gambit's logit $\alpha$-tracing procedure on the full game---not restricted to the winning component---starting from the uniform prior. 
We follow the path to $\alpha=1$ and take the resulting profile as the candidate equilibrium. 
To guard against numerical asymmetries, we then enforce symmetry in the reported profile by setting $\sigma^{r}=\sigma^{c}$ equal to the traced row strategy.
Because the prior and the game are symmetric, the traced profile is generically symmetric; the coercion is a safeguard.
\item \emph{Deviation~2 (singleton asymmetric case).} If the winning
component is a singleton asymmetric equilibrium, we run the same
$\alpha$-tracing procedure and then report the coerced symmetric profile as above. 
If the tracing routine raises an exception, the unique equilibrium is returned unchanged.
\end{itemize}

\renewcommand{\thefigure}{D\arabic{figure}} 
\setcounter{figure}{0}  

\renewcommand{\thetable}{D\arabic{table}} 
\setcounter{table}{0}  
